CommonMind Consortium: DLPFC

### 2020-09-22 combined_analysis/diff.networks.Rmd
Update diff networks

```{r modules.in.second.cohort, fig.width=8, fig.height=25}

@@

	ggplot(res, aes(Test, -log10(PValue))) + geom_bar(stat="identity", fill=res$Geneset[1]) + coord_flip() + theme_bw() + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5))  + scale_y_continuous(expand=c(0,0), lim=c(0, lim*1.05)) + ggtitle(module) + geom_hline(yintercept=-log10(0.05), color="red", linetype="dashed")
}) 
plot_grid(plotlist = figList, ncol=1)
```

@@

```{r modules.in.discovery.Dx_Sex, fig.width=10, fig.height=50}

@@

# i = which(df_cohort2$FDR < 0.1) 
i = 1:5

>>>>

```{r modules.in.second.cohort, fig.width=8, fig.height=50}

@@

	ggplot(res, aes(Test, -log10(PValue))) + geom_bar(stat="identity", fill=res$Geneset[1]) + coord_flip() + theme_bw() + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5))  + scale_y_continuous(expand=c(0,0), lim=c(0, lim*1.05)) + ggtitle(module) + geom_hline(yintercept=-log10(0.05), color="red", linetype="dashed") + ylab(bquote(-log[10]~P))
}) 
plot_grid(plotlist = figList, ncol=1)
```

@@

```{r modules.in.discovery.Dx_Sex, fig.width=8, fig.height=50}

@@

# i = which(df_cohort2$FDR < 0.1) 
i = 1:2
